Algorithm explanation

### 2013-04-18 article/algo.tex
Explanation of DAG-splitting * Equivalent to copying constraints

The solution of $G$ is a map $\rho$ from predicate variables to linear
predicates of the form $\lambda x_1, \cdots ,x_n. \psi $ (where $\psi$
is a formula constructed from
\begin{align*}
\psi ::= &a_1 x_1 + \cdots + a_n x_n \leq b \vert \\ &\psi \wedge \psi
\vert \psi \vee \psi \vert true \vert false
\end{align*}
), where $\rho[G]$ is a tautology. A solution is \textit{simple} if
$\rho[P]$ is of the form $a_1 x_1 + \cdots + a_n x_n \leq b$ for every
$P$ in $dom(\rho)$.

@@

\begin{align*}
\left\lbrace
 \mathbf{a} \mathbf{x} \leq b |
 \exists \left( FV(C)
  \setminus (\mathbf{a} \cup \left\lbrace b \right\rbrace
 \right). C
\right\rbrace
\end{align*}

@@

\quote
If $\models \sigma(C_\star)$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) |
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\endquote

>>>>

The solution of $G$ is a map $\rho$ from predicate variables to linear
predicates of the form $\lambda x_1, \cdots ,x_n. \psi $ (where $\psi$
is a formula constructed from
\begin{align*}
\psi ::= & a_1 x_1 + \cdots + a_n x_n \leq b \mid \\
& \psi \wedge \psi \mid \psi \vee \psi \mid true \mid false
\end{align*}
), where $\rho[G]$ is a tautology. A solution is \textit{simple} if
$\rho[P]$ is of the form $a_1 x_1 + \cdots + a_n x_n \leq b$ for every
$P$ in $dom(\rho)$.

@@

\begin{align*}
\left\lbrace
 \mathbf{a} \mathbf{x} \leq b \middle|
 \exists \left( FV(C)
  \setminus (\mathbf{a} \cup \left\lbrace b \right\rbrace
 \right). C
\right\rbrace
\end{align*}

@@

\begin{quote}
If $\models \sigma(C_\star)$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\end{quote}

If $C_\star$ is unsatisfiable, there are two possibility for them.

\begin{itemize}
\item No solution exists for $G$.
\item No simple solution exists for $G$.
\end{itemize}

If $G$ has node(s) which has multiple successors, the second case is
possible. We now consider to give a solution to the such case.

Let $\hat u$ be the (least) vertex on $<^+$ with multiple successors
denoted by $succ(u)$. For each $v_i \in succ(u)$, we transform the graph
$G$ with the following operation:

\begin{align*}
\frac{
(u, v_i) \in E \wedge \varphi(u) = P(\mathbf{x}) \wedge
\Delta(u) = \left( \mathbf{a} \mathbf{x} \leq b, C \right)
}{
\begin{aligned}
E & := { (u, v_i'), (v_i', v_i) } \cup ( E \setminus (u, v_i) ) \\
\varphi(v_i') & := P_i(\mathbf{x}) \\
\Delta(v_i') & := \left( \mathbf{a}' \mathbf{x} \leq b', \textsc{Copy}(C) \right)
\end{aligned}
}
\end{align*}

The $\textsc{Copy}$ duplicates a given linear constraint by renaming
all variables to fresh ones. $\mathbf{a'}$ and $b'$ are renamed
variables from $\mathbf{a}$ and $b$ respectively.

Obtaining $G'$ after the transformation above, if $C_{v_\bot}$ becomes
satisfiable, a solution $\rho$ to $G$ is given by using solution
$\rho'$ to $G'$:

\begin{align*}
 \rho = \rho' \cup \left\lbrace P = \bigwedge_i \rho'[P_i] \middle|
 \varphi(\hat u) = P(\mathbf{x}) \right\rbrace
\end{align*}

Note that predicate variables on greater nodes than $\hat u$ may
also have duplicated assignments, which should be combined in the
same manner as $P$ above.

If $C_{v_\bot}$ stays unsatisfiable in $G'$, we can repeat the
transformation until no vertices have multiple successors.
